Enhancing the prediction of sales for newly published books by means of computational intelligence methods

### 2016-05-05 paper.tex
Discussing M5P models

@@

In this section we show the output of one of the models built during the regression, namely we present one of the decision trees generated by M5P method, to demonstrate the value of the proposal to generate an useful decision-aid tool for and expert (publisher) to see what sales can be expected for the different values of the input variables (including the print-run).

%***TO DO:*** better explain this
% Sam will do it

We have considered the publisher that sells the most as a good example case to show.

Figure \ref{fig:decision_tree_best_seller} depicts the obtained decision tree for the best seller publishing company (UDL929). The leaves correspond to linear regression models that can be computed (easily) to get the final predicted value for book sales. This tree has been created considering the 10 pre-sales features.

@@

%***TO DO***: comments on the figure\\

Figure \ref{fig:decision_tree_best_seller_fs} shows the decision tree obtained for the same publishing company (the same data, but just considering the selected features by ReliefAttributeEval method, since it is the one which yields the best results).

%***TO DO***: better justify this\\

@@

%***TO DO***: comments on the figure\\

@@

Case 1-A: Developing prediction models to predict Total sales for
PublishingCo704 with CfsSubsetEval feature selection.

@@

Case 1-A: Developing prediction models to predict Total sales for
PublishingCo704 with SOM feature selection.

@@

Case 1-B: Developing prediction models to predict Total sales for
PublishingCo-UDLU11 with CfsSubsetEval feature selection.

@@

Case 1-B: Developing prediction models to predict Total sales for
PublishingCo-UDLU11 with SOM feature selection.

@@

Case 2-A: Developing prediction models to predict Total sales for
PublishingCo-UDL929 with CfsSubsetEval feature selection.

@@

Case 2-A: Developing prediction models to predict Total sales for
PublishingCo-UDL929 with SOM feature selection.

@@

Case 2-B: Developing prediction models to predict Total sales for
PublishingCo-UDLW12 with CfsSubsetEval feature selection.

@@

Case 2-B: Developing prediction models to predict Total sales for
PublishingCo-UDLW12 with SOM feature selection.

>>>>

% [pedro] La cosa es que esta gente toma libros ya publicados y de los que tienen todos los datos de ventas para analizar y obtener patrones de ventas. Nosotros trabajamos con datos de libros que ni siquiera se han impreso aún, por lo que no tenemos ni idea de cómo van a funcionar. Esta gente dispone de datos de ventas, mientras que nosotros sólo vamos a tener datos relativos a "¿dónde lo vas a poner a la venta?" o "¿vas a dar algún regalo para intentar vender más?" (cosas así).

@@

In this section we show the output of one of the models built during the regression, namely we present two of the decision trees generated by M5P method, to demonstrate the value of the proposal to generate a useful decision-aid tool for and expert (publisher) to see what sales can be expected for the different values of the input variables (including the print-run). The first decision tree is considered for the publisher that sells the most. Figure \ref{fig:decision_tree_best_seller} depicts the decision tree for the best seller publishing company (UDL929). The leaves correspond to linear regression models that can be computed (easily) to get the final predicted value for book sales. The second decision tree is for the same publishing company (the same data, but just considering the selected features by RAE method, since it is the one which yields the best results). The latter tree is shown in Figure \ref{fig:decision_tree_best_seller_fs}.

Examining both decision trees, it can be noticed that the \texttt{tot\_points\_sale} variable appeared twice in the tree and one of them was at the root. This indicates that the total number of points of sale has a major role in forecasting the total sales. We can also notice that \texttt{distrib\_novelty} appears at the top of the trees at a higher level compared to the \texttt{ret\_price} variable. In addition, both tree models reveal that marketing variables such as the total number of points of sale and the number of units distributed as novelty have higher influence on the prediction than the selling price of the book. This interpretation leads us to suggest that companies could probably improve the accuracy of their sales forecasting models by incorporating more marketing related variables in their models.

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@
